---
title: "Spotify Viz"
author: "Oscar Leal 1903161"
date: "2/16/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE}
library(data.table)
library(ggplot2)
theme_set(theme_minimal()) # set global theme for ggplot
```

## Reading the data from TidyTuesdays, and exploring.

```{r, echo=TRUE, message=TRUE}
spotify_songs <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-01-21/spotify_songs.csv')

tail(spotify_songs)
typeof(spotify_songs)
spotify_songs <- as.data.table(spotify_songs)

```
```{r, echo = TRUE}
skimr::skim(spotify_songs)
```

After skimming the data we can say we have a nice distribution of numeric and character type variables. 

It was interesting to find the variable *danceability* as a value to determine how danceable is a song from 0.0 to 1.0, and how the mean tends to be positive!
*Energy* was also positive. 

There are some rows with long album names, songs and playlist. 

We will convert *key* to factor! Since they are values resembling the overall key of a track. 

```{r, echo = TRUE}
unique(spotify_songs$key)

spotify_songs$key <- as.factor(spotify_songs$key)

# Dropping NA values. 5 occurrences, no need to keep!
spotify_songs <- spotify_songs[!(is.na(track_name) & is.na(track_artist) & is.na(track_album_name))]

length(unique(spotify_songs$track_name)) - nrow(spotify_songs)

toprepeated <- head(spotify_songs[, .(count = .N), by = track_id][count > 1][order(-count)])

topsongsrepeated <- spotify_songs[track_id %in% c(toprepeated$track_id), c('track_name', 'track_artist', 'track_album_name', 'playlist_name', 'playlist_id')][order(track_artist)]

unique(topsongsrepeated$track_artist)


```

It also seems that there are repeating songs, since there are only 23449 unique values out of 32828 (not including the 5 NAs).

The artists that have repeated songs are Kygo, Riton, The Chainsmokers and Travis Scott, the same song appears in different playlists.
Kygo even has two songs that are commonly added to playlists!



Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
